Paper Report

### 2017-12-07 Paper_report.tex
Save

\usepackage{graphicx} % Required for the inclusion of images
\usepackage{natbib} % Required to change bibliography style to APA
\usepackage{amsmath} % Required for some math elements

@@

@@

>>>>

\usepackage{graphicx} % Required for the inclusion of images
\usepackage{natbib} % Required to change bibliography style to APA
\usepackage{amsmath} % Required for some math elements 
\usepackage[]{algorithm2e}

@@

\begin{equation}
J(\theta) = \sum_{j=1}^J \sum_{a_j} p_{\theta'}(a_j|f_j) \, \bigtriangledown log \, p_{\theta}(f_j | e_{a_j}) \quad + p_{\theta'}(a_j, a_{j-1}|f_j) \, \bigtriangledown log \, p_{\theta}(a_j | a_{j-1})  ] 
\label{Word Alignment Model Neural Network Gradient}
\end{equation}

@@

\section{HMM-NN Experiment}
\subsection{Model 1: Simple NN-based Emission}
We review the equation \eqref{Word Alignment Model Neural Network Gradient}.

\begin{equation}
J(\theta) = \sum_{j=1}^J \sum_{a_j} p_{\theta'}(a_j|f_j) \, \bigtriangledown log \, p_{\theta}(f_j | e_{a_j}) \quad
\end{equation}

\begin{itemize}
\item \textbf{Emission matrix }$p_{\theta}(f_j | e_{a_j})$: We receive the target-language sentence and return the probabilities for all source-language vocabulary under Feed-Forward NN.

\item \textbf{Emission posterior} $p_{\theta'}(a_j|f_j)$ : We set source-language sentence as a set of observation, Baum-Welch algorithm returns forward and backward messages with size (J * I)

\item \textbf{Transition matrix} $p_{\theta}(a_j | a_{j-1})$: This matrix does not depend on the source-language and the target-language sentence. It depends on a set of jump distance.
	\begin{enumerate}
	\item Initialize jump distance set.
	\item Create transition matrix T with size (I * J) from this jump distance set.
	\item Create initial transition matrix  T0 with size (1 * I) randomly
	\item Calculate forward and backward message from NN-based emission matrix, transition matrix T and intial transition matrix T0.
	\item Emission posterior is forward * backward message (See\cite{Tran16unsupervised})
	\end{enumerate}
\end{itemize}

\begin{algorithm}[H]
\textbf{Input:}\\
	\begin{itemize}
	\item Source sentence: $f_1^J = f_1,...,f_j,...f_J$
	\item Target sentence: $e_1^I = f_1,...,f_i,...f_I$
	\end{itemize}
\textbf{Initialization:} \\
	\begin{itemize}
	\item Initialize jump distance set JD
	\end{itemize}
\textbf{Training:} \\
\While{each sentence pair $(f_1^J, e_1^I)$ in Training set}{
	\begin{enumerate}
	\item Get Emission matrix E with size $(I * V_{F})$ from NN
	\item Get Transition matrix T $(I * I)$ from \textbf{JD}
	\item Select randomly Initial transition matrix T0 with $(1 * I)$
	\item Get forward $\alpha$ and backward $\beta$ message with size $(J*I)$
	\item Get Emission posterior $EP = \alpha * \beta $, Normalize EP and Reshape EP with size $(I * V_{F})$
	\item Get expected-T $(I * I)$ from E, T, $\alpha$, $\beta$
	\item Update \textbf{JD} from expected-T
	\end{enumerate}

 }
 \textbf{Validation:} \\
 \While{each sentence pair $(f_1^J, e_1^I)$ in Validation set}{
	\begin{enumerate}
	\item Get Emission matrix E with size $(I * V_{F})$ from NN
	\item Get Transition matrix T $(2I * 2I)$ with Null tokens from \textbf{JD}
	\item Select randomly Initial transition matrix T0 with $(1 * 2I)$
	\item Get location pair $(J * 2I)$ with Viterbi from E with size $(2I * V_{F})$ and T with $(2I * 2I)$
	\item Calculate AER
	\end{enumerate}

 }

 \caption{Model 1}
\end{algorithm}
